Paper_analyses

### 2021-07-23 Paper_Analyses_subj_obje_arousal.Rmd
pupil and velocity analyses
fixed #1  and included corrections for timeseries (holm).

next need to decide on whether significance is tested based on uncorrected values using a simple  (e.g. at least 3 consecutive samples <.05, or relying on the correction adjusted. the downside of the latter is that it might be quite conservative.

Random effects:
 Groups   Name                Variance Std.Dev. Corr       
 ssid     (Intercept)         0.78415  0.8855              
          Mean_gray_z         0.13611  0.3689   0.55       
 ssid.1   valence_c           0.04233  0.2057              
          arousal_c           0.02296  0.1515    0.89      
          valence_c:arousal_c 0.01700  0.1304   -0.19  0.01
 Residual                     2.57999  1.6062              
Number of obs: 2185, groups:  ssid, 43

Fixed effects:
                    Estimate Std. Error       df t value             Pr(>|t|)    
(Intercept)         -0.66764    0.14166 44.77819  -4.713          0.000023962 ***
valence_c            0.08546    0.06557 28.33677   1.303              0.20294    
arousal_c            0.44137    0.06445 22.53213   6.848          0.000000619 ***
Mean_gray_z         -0.96311    0.06622 43.35750 -14.544 < 0.0000000000000002 ***
valence_c:arousal_c  0.15461    0.04434 24.37046   3.487              0.00187 ** 
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

@@

let's test the interaction term
<!-- 30 bins -->
```{r}

@@

range(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin_no)
nbins<- unique(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin_no)
nrow(nbins)
nbins = 30 # number of bins

# create and empty dataframe for the timecourse analyses
timecourse_result_df_int <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))

@@

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            lmer_bin_pup_summary
            # lmer_bin_pup_summary[["coefficients"]][3,1]
            timecourse_result_df_int[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
            timecourse_result_df_int[i,2]<- lmer_bin_pup_summary[["coefficients"]][5,1] # first number is term(row), second is column
            timecourse_result_df_int[i,3]<-lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
            timecourse_result_df_int[i,4]<-lmer_bin_pup_summary[["coefficients"]][5,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_result_df_int[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

@@

# create and empty dataframe for the timecourse analyses
timecourse_60bin_result_df <- data.frame(timebins= rep(NA, 60), Estimate= rep(NA, 60), 
                                   t=rep(NA, 60), p=rep(NA, 60), cov= as.character(rep(NA,60)))

@@

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
        lmer_bin_pup  <- lmer(pup_basCor ~ (arousal_c* valence)+Mean_gray_z  +
                                (1 | ssid),
                                # (0 +arousal_c* valence | ssid),
                                # (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
                                    # mediansplit_self_valence == "More positive" & 
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            lmer_bin_pup_summary
            # lmer_bin_pup_summary[["coefficients"]][3,1]
            timecourse_60bin_result_df[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] #save the exact value of time bin
            timecourse_60bin_result_df[i,2]<-
              lmer_bin_pup_summary[["coefficients"]][4,1] 
            # first number is term(row), second is column
            timecourse_60bin_result_df[i,3]<-
              lmer_bin_pup_summary[["coefficients"]][4,4] # t statistic
            timecourse_60bin_result_df[i,4]<-
              lmer_bin_pup_summary[["coefficients"]][4,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_60bin_result_df[i,5] <-
              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

@@

timecourse_60bin_result_df %>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

@@

Pupil velocity test

velocity analyses
```{r}
# thought maybe it has soemthing to to with the velcity, velocity is sidderent

install.packages("pspline")
library(pspline)

@@

>>>>

Random effects:
 Groups   Name                Variance Std.Dev. Corr       
 ssid     (Intercept)         0.78415  0.8855              
          Mean_gray_z         0.13611  0.3689   0.55       
 ssid.1   valence_c           0.04233  0.2057              
          arousal_c           0.02296  0.1515    0.89      
          valence_c:arousal_c 0.01700  0.1604   -0.19  0.01
 Residual                     2.57999  1.6062              
Number of obs: 2185, groups:  ssid, 43

Fixed effects:
                    Estimate Std. Error       df t value             Pr(>|t|)    
(Intercept)         -0.66764    0.14166 44.77819  -4.713          0.000023962 ***
valence_c            0.08546    0.06557 28.33677   1.603              0.20294    
arousal_c            0.44137    0.06445 22.53213   6.848          0.000000619 ***
Mean_gray_z         -0.96311    0.06622 43.35750 -14.544 < 0.0000000000000002 ***
valence_c:arousal_c  0.15461    0.04434 24.37046   3.487              0.00187 ** 
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

@@

Pupil changes over time
<!-- 30 bins -->
```{r}

@@

range(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin_no)

nbins<- unique(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin_no)
nrow(nbins)
# nbins = 30 # number of bins

# create and empty dataframe for the timecourse analyses
timecourse_result_df_int <- data.frame(timebins= rep(NA, 30), 
                                       Estimate_ar= rep(NA, 30), 
                                       t_ar=rep(NA, 30), 
                                       p_ar=rep(NA, 30),
                                       Estimate_vl= rep(NA, 30), 
                                       t_vl=rep(NA, 30), 
                                       p_vl=rep(NA, 30),
                                       Estimate_br= rep(NA, 30), 
                                       t_br=rep(NA, 30), 
                                       p_br=rep(NA, 30),
                                       Estimate_ar_vl= rep(NA, 30), 
                                       t_ar_vl=rep(NA, 30), 
                                       p_ar_vl=rep(NA, 30),
                                       cov= as.character(rep(NA,30)))

@@

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            lmer_bin_pup_summary
            # lmer_bin_pup_summary[["coefficients"]][3,1]
            timecourse_result_df_int[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin

            timecourse_result_df_int[i,2]<- lmer_bin_pup_summary[["coefficients"]][5,1] # first number is term(row), second is column
            timecourse_result_df_int[i,3]<-lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
            timecourse_result_df_int[i,4]<-lmer_bin_pup_summary[["coefficients"]][5,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_result_df_int[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

@@

# create and empty dataframe for the timecourse analyses
timecourse_60bin_result_df <- data.frame(timebins= rep(NA, 60), 
                                       Estimate_ar= rep(NA, 60), 
                                       t_ar=rep(NA, 60), 
                                       p_ar=rep(NA, 60),
                                       Estimate_vl= rep(NA, 60), 
                                       t_vl=rep(NA, 60), 
                                       p_vl=rep(NA, 60),
                                       Estimate_br= rep(NA, 60), 
                                       t_br=rep(NA, 60), 
                                       p_br=rep(NA, 60),
                                       Estimate_ar_vl= rep(NA, 60), 
                                       t_ar_vl=rep(NA, 60), 
                                       p_ar_vl=rep(NA, 60),
                                       cov= as.character(rep(NA,60)))

@@

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
        lmer_bin_pup  <- lmer(pup_basCor ~ (arousal_c* valence)+Mean_gray_z  +
                                (1 | ssid),
                                # (0 +arousal_c* valence | ssid),
                                # (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            lmer_bin_pup_summary
            # lmer_bin_pup_summary[["coefficients"]][3,1]
            timecourse_60bin_result_df[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
            #save the exact value of time bin
            # store arousal (2,parameter)            # first number is term(row), second is column
            timecourse_60bin_result_df[i,2]<-
            lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
            timecourse_60bin_result_df[i,3]<-
              lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_60bin_result_df[i,4]<-
            lmer_bin_pup_summary[["coefficients"]][2,5] # p value

            # valence

            timecourse_60bin_result_df[i,5]<-
            lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
            timecourse_60bin_result_df[i,6]<-
              lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
            timecourse_60bin_result_df[i,7]<-
              lmer_bin_pup_summary[["coefficients"]][3,5] # p value

            # brighteness

            timecourse_60bin_result_df[i,8]<-
            lmer_bin_pup_summary[["coefficients"]][4,1] #estimate
            timecourse_60bin_result_df[i,9]<-
              lmer_bin_pup_summary[["coefficients"]][4,4] # t statistic
            timecourse_60bin_result_df[i,10]<-
              lmer_bin_pup_summary[["coefficients"]][4,5] # p value

            # interaction arousal x brighteness

            timecourse_60bin_result_df[i,11]<-
            lmer_bin_pup_summary[["coefficients"]][5,1] #estimate
            timecourse_60bin_result_df[i,12]<-
              lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
            timecourse_60bin_result_df[i,13]<-
              lmer_bin_pup_summary[["coefficients"]][5,5] # p value

            timecourse_60bin_result_df[i,14] <-
              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

@@

  # geom_hline(yintercept = .05, color = 'red', size = 1.5)

# adjust p values and tag as TRUE whenevee there is at least 3 consecutive p values below .05
?p.adjust
timecourse_60bin_result_df$p_ar_adj<- p.adjust(timecourse_60bin_result_df$p_ar, method = "holm")
timecourse_60bin_result_df$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df$p_ar_adj<.05, TRUE, FALSE)

timecourse_60bin_result_df$p_vl_adj <- p.adjust(timecourse_60bin_result_df$p_vl, method = "holm")
timecourse_60bin_result_df$p_vl_adj_TRUE<- if_else(timecourse_60bin_result_df$p_vl_adj<.05, TRUE, FALSE)

timecourse_60bin_result_df$p_br_adj <- p.adjust(timecourse_60bin_result_df$p_br, method = "holm")
timecourse_60bin_result_df$p_br_adj_TRUE<- if_else(timecourse_60bin_result_df$p_br_adj<.05, TRUE, FALSE)

timecourse_60bin_result_df$p_ar_vl_adj <- p.adjust(timecourse_60bin_result_df$p_ar_vl, method = "holm")
timecourse_60bin_result_df$p_ar_vl_adj_TRUE<- if_else(timecourse_60bin_result_df$p_ar_vl_adj<.05, TRUE, NULL)

# find the first and last true in a sequence of TRUES
duplicated(timecourse_60bin_result_df$p_ar_adj_TRUE, na.rm = TRUE)

?linetype
timecourse_60bin_result_df %>%
  ggplot(aes(timebins, Estimate_ar_vl))+
  geom_line(size = 1)+
  geom_line(aes(y = Estimate_vl), linetype = "dashed", size = 1)+
  geom_line(aes(y = Estimate_br), linetype = "dotted", size = 1)+
  geom_line(aes(y = Estimate_ar_vl), linetype = "dotdash", size = 1, color = "red")

timecourse_60bin_result_df %>%
  ggplot(aes(timebins, t_ar))+
  geom_line(size = 1)+
  geom_line(aes(y = t_vl), linetype = "dashed", size = 1)+
  # geom_line(aes(y = t_br), linetype = "dotted", size = 1)+
  geom_line(aes(y = t_ar_vl), linetype = "dotdash", size = 1, color = "red")

@@

Pupil velocity test
# velocity analyses

```{r}
# install.packages("pspline")
library(pspline)

@@

velocity timecourse
```{r}
# let's test the interaction term
nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
range(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)

# create and empty dataframe for the timecourse analyses
timecourse_60bin_result_df_vel <- data.frame(timebins= rep(NA, 60), 
                                       Estimate_ar= rep(NA, 60), 
                                       t_ar=rep(NA, 60), 
                                       p_ar=rep(NA, 60),
                                       Estimate_vl= rep(NA, 60), 
                                       t_vl=rep(NA, 60), 
                                       p_vl=rep(NA, 60),
                                       Estimate_br= rep(NA, 60), 
                                       t_br=rep(NA, 60), 
                                       p_br=rep(NA, 60),
                                       Estimate_ar_vl= rep(NA, 60), 
                                       t_ar_vl=rep(NA, 60), 
                                       p_ar_vl=rep(NA, 60),
                                       cov= as.character(rep(NA,60)))

# i =1
tmp.df4_full_stim_downs_jun2021_60bins$pup_vel_smooth

tmp.df4_full_stim_downs_jun2021_60bins$pup_vel_smooth

nbins<- nbins[3:56]

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
        lmer_bin_pup  <- lmer(pup_vel_smooth ~ (arousal_c* valence)+Mean_gray_z  +
                                (1 | ssid),
                                # (0 +arousal_c* valence | ssid),
                                # (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
                                    !is.na(pup_vel_smooth)&
                                    timebin_no == nbins[b]))

        # store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            lmer_bin_pup_summary
            # lmer_bin_pup_summary[["coefficients"]][3,1]
            timecourse_60bin_result_df_vel[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
            #save the exact value of time bin
            # store arousal (2,parameter)            # first number is term(row), second is column
            timecourse_60bin_result_df_vel[i,2]<-
            lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
            timecourse_60bin_result_df_vel[i,3]<-
              lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_60bin_result_df_vel[i,4]<-
            lmer_bin_pup_summary[["coefficients"]][2,5] # p value

            # valence

            timecourse_60bin_result_df_vel[i,5]<-
            lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
            timecourse_60bin_result_df_vel[i,6]<-
              lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
            timecourse_60bin_result_df_vel[i,7]<-
              lmer_bin_pup_summary[["coefficients"]][3,5] # p value

            # brighteness

            timecourse_60bin_result_df_vel[i,8]<-
            lmer_bin_pup_summary[["coefficients"]][4,1] #estimate
            timecourse_60bin_result_df_vel[i,9]<-
              lmer_bin_pup_summary[["coefficients"]][4,4] # t statistic
            timecourse_60bin_result_df_vel[i,10]<-
              lmer_bin_pup_summary[["coefficients"]][4,5] # p value

            # interaction arousal x brighteness

            timecourse_60bin_result_df_vel[i,11]<-
            lmer_bin_pup_summary[["coefficients"]][5,1] #estimate
            timecourse_60bin_result_df_vel[i,12]<-
              lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
            timecourse_60bin_result_df_vel[i,13]<-
              lmer_bin_pup_summary[["coefficients"]][5,5] # p value

            timecourse_60bin_result_df_vel[i,14] <-
              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

     i = i+1
}
# timecourse_result_df_pos<- timecourse_result_df
View(timecourse_60bin_result_df_vel)

timecourse_60bin_result_df_vel %>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

View(timecourse_60bin_result_df_vel)
timecourse_60bin_result_df_vel %>%
  ggplot(aes(timebins, Estimate_ar))+
  geom_line(size = 1)+
  geom_line(aes(y = Estimate_vl), linetype = "dashed", size = 1)+
  geom_line(aes(y = Estimate_br), linetype = "dotted", size = 1)+
  geom_line(aes(y = Estimate_ar_vl), linetype = "dotdash", size = 1, color = "red")+
  ylim(-.1,.25)

# adjust p values and tag as TRUE whenevee there is at least 3 consecutive p values below .05
?p.adjust
timecourse_60bin_result_df_vel$p_ar_adj<- p.adjust(timecourse_60bin_result_df_vel$p_ar, method = "holm")
timecourse_60bin_result_df_vel$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df_vel$p_ar_adj<.05, TRUE, FALSE)

timecourse_60bin_result_df_vel$p_vl_adj <- p.adjust(timecourse_60bin_result_df_vel$p_vl, method = "holm")
timecourse_60bin_result_df_vel$p_vl_adj_TRUE<- if_else(timecourse_60bin_result_df_vel$p_vl_adj<.05, TRUE, FALSE)

timecourse_60bin_result_df_vel$p_br_adj <- p.adjust(timecourse_60bin_result_df_vel$p_br, method = "holm")
timecourse_60bin_result_df_vel$p_br_adj_TRUE<- if_else(timecourse_60bin_result_df_vel$p_br_adj<.05, TRUE, FALSE)

timecourse_60bin_result_df_vel$p_ar_vl_adj <- p.adjust(timecourse_60bin_result_df_vel$p_ar_vl, method = "holm")
timecourse_60bin_result_df_vel$p_ar_vl_adj_TRUE<- if_else(timecourse_60bin_result_df_vel$p_ar_vl_adj<.05, TRUE, NULL)

# find the first and last true in a sequence of TRUES
duplicated(timecourse_60bin_result_df_vel$p_ar_adj_TRUE, na.rm = TRUE)
